### 2024-09-05 download-football-data.qmd
20240905 - D/ST points bracket

# Defense/Special Teams
scoring_obj$pts_bracket[[3]]$threshold <- 13
scoring_obj$pts_bracket[[3]]$points <- 4

scoring_obj$pts_bracket[[4]]$threshold <- 20
scoring_obj$pts_bracket[[4]]$points <- 1

scoring_obj$pts_bracket[[5]]$threshold <- 27
scoring_obj$pts_bracket[[5]]$points <- 0

scoring_obj$pts_bracket[[6]] <- list(
  threshold = 34,
  points = -1
)

scoring_obj$pts_bracket[[7]] <- list(
  threshold = 99,
  points = -4
)
```

>>>>

# Defense/Special Teams
scoring_obj$pts_bracket <- list(
  list(threshold = 0, points = 10),
  list(threshold = 6, points = 7),
  list(threshold = 13, points = 4),
  list(threshold = 20, points = 1),
  list(threshold = 27, points = 0),
  list(threshold = 34, points = -1),
  list(threshold = 99, points = -4)
)
```
